A unified pseudo-$C_\ell$ framework

### 2018-08-31 doc/Paper/main.tex
added last timing figure

     Not all parts of the power spectrum estimation take the same amount of time. E.g. even though the scaling with $\ell_{\rm max}$ is the same, the computation of the mode-coupling matrix typically takes longer than a performing single SHT. Computation times can be significantly increased if deprojection over a large number of maps is required or if $E/B$ purification is required. The bottom panel of Figure \ref{fig:scaling_lmax} shows the execution times associated to the most relevant types of operations:

     \begin{figure}
     \centering
     \includegraphics[width=0.99\columnwidth]{time_scaling}
     \includegraphics[width=0.99\columnwidth]{timing}
     \caption{Computing time for the auto-power spectra of curved-sky spin-0 (data 00, hollow circles), and spin-2 (data 22, solid triangles) contamination-free maps, as wells as their cross-power (data 02, solid circles) as a function of $\ell_{max}$. We include the expected scaling for the pseudo-$C_{\ell}$ estimator (solid line) and force it to go through the point for the spin-0 auto-power at $\ell=96$ showing remarkable agreement.}
     \label{fig:scaling_lmax}
     \end{figure}

>>>>

     Not all parts of the power spectrum estimation take the same amount of time. E.g. even though the scaling with $\ell_{\rm max}$ is the same, the computation of the mode-coupling matrix typically takes longer than a performing single SHT. Computation times can be significantly increased if deprojection over a large number of maps is required or if $E/B$ purification is required. The bottom panel of Figure \ref{fig:scaling_lmax} shows the execution times associated to the most relevant types of operations. These are (using the labels provided in the figure):
     \begin{itemize}
       \item {\bf Field $s=0$ and $s=2$}: generating a {\tt NmtField} object. This entails taking the SHT of a given spin-0 or 2 map as well as that of its associated weights map.
       \item {\bf Deproj.}: generating a {\tt NmtField} object with contaminant deprojection. This is the same as the above in addition to computing the SHT of a set of contaminant templates. In this case we include 5 templates, and the additional computation time will increase linearly with the number of templates.
       \item {\bf Purification}: generating a {\tt NmtField} object with $B$-mode purification. This is the same as ``Field $s=2$'' in addition to computing the pure $B$-modes. This entails estimating a more accurate SHT of the apodized mask as well as a combination of harmonic-space and real-space operations described in Section \ref{ssec:maths.pureb}.
       \item {\bf Deproj. $+$ purif.}: generating a {\tt NmtField} object with both $B$-mode purification and contaminant deprojection. This entails all of the operations implied by ``Deproj.'' and ``Purification'' in addition to the computation of the $B$-mode-purified templates (see Eqs. \ref{eq:dp.g.aux} and \ref{eq:dp.f.aux}).
       \item {\bf MCM $s_1$-$s_2$}: generating the pseudo-$C_\ell$ mode-coupling matrix for a spin-$s_1$ field and a spin-$s_2$ field.
     \end{itemize}
     The times reported in this figure correspond to the time required to perform a single instance of the corresponding operation for fields with resolution $N_{\rm side}=1024$ using 16 \texttt{OpenMP} threads. Note that, even though the computation of the mode-coupling matrix dominates the total execution time in the simplest scenarios, in the most complex situation, involving both purification and deprojection, setting up a single field can take significantly longer.

     \begin{figure}
       \centering
       \includegraphics[width=0.99\columnwidth]{time_scaling}
       \includegraphics[width=0.99\columnwidth]{timing}
       \caption{{\sl Top panel}: computing time for the auto-power spectra of curved-sky spin-0 (data 00, hollow circles), and spin-2 (data 22, solid triangles) contamination-free maps, as wells as their cross-power (data 02, solid circles) as a function of $\ell_{\rm max}$. We include the expected scaling $\propto\ell_{\rm max}$ for the pseudo-$C_{\ell}$ estimator (solid red line) for comparison. {\sl Bottom panel:} execution time for different tasks associated with the pseudo-$C_\ell$ estimator. We show times for fields with resolution $N_{\rm side}=1024$, which can be extrapolated to other resolutions using a $\propto N_{\rm side}^3$ scaling, as described above. The description of the different tasks shown is given in the main text.}\label{fig:scaling_lmax}
     \end{figure}
